Consensus cell types across osteosarcoma samples

### 2025-02-11 analyses/cell-type-consensus/exploratory-notebooks/03-osteosarcoma-consensus-celltypes.Rmd

    stacked_barchart(
      df,
      fill_column = "immune_category",
      facet_variable = category,
      celltype_colors = three_color_scheme
    )
}) |>
  patchwork::wrap_plots(ncol = 1, guides = "collect") + 
    patchwork::plot_annotation(tag_levels = list(metadata_categories))

@@

    stacked_barchart(
      df,
      fill_column = "top_celltypes",
      facet_variable = category,
      celltype_colors = all_celltype_colors
    )
  }) |>
  patchwork::wrap_plots(ncol = 1, guides = "collect")
```

>>>>

    stacked_barchart(
      df,
      fill_column = "immune_category",
      facet_variable = category,
      celltype_colors = three_color_scheme
    ) +
      labs(title = category)
}) |>
  patchwork::wrap_plots(ncol = 1, guides = "collect")

@@

    stacked_barchart(
      df,
      fill_column = "top_celltypes",
      facet_variable = category,
      celltype_colors = all_celltype_colors
    ) +
      labs(title = category)
  }) |>
  patchwork::wrap_plots(ncol = 1, guides = "collect")
```
